Fast Radio Burst Cosmology

### 2014-05-22 writeup/dm_angular_ps.tex
Partially working script.
Wrote short road to sensitivity.

@@

>>>>

\red{$D^{\bar{n}_e}_i$ and $D^{\rm src}_i$ are likely correlated due to
    redshift evolution of source events, but this does not affect the
    measurement since both are treated as noise terms.}

@@

\section{Short road to sensitivity}

The errorbar on the redshift averaged dispersion measure angular power spectrum
is
\begin{equation}
    \sigma_{C_l} = \sqrt{\frac{2}{(2 l + 1) f_{\rm sky}}} (C_l + C^N_l),
\end{equation}
where the noise power spectrum is
\begin{equation}
    C^N_l = \frac{4 \pi \sigma_D^2 \sqrt{f_{\rm sky}}}{N_{\rm FRB}}.
\end{equation}
Here $N_{\rm FRB}$ is the number of dispersion measures measured from fast
radio bursts. \red{I'm only 80\% sure about the factors of $f_{\rm sky}$}.

$\sigma_D^2$ is the variance of the dispersion measures.  This would in
practice be measured directly from the observed set, but in terms of
theoretical parameters is
\begin{equation}
\sigma_D^2 = \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src} + \int \ud z \ud z'
\delta(z - z') p(z) w^{z z'}(1),
\end{equation}
where the first two terms are defined above. The third term is likely
neglidgable and could also be written as
\begin{equation}
    \int \ud z \ud z' \delta(z - z') p(z) w^{z z'}(1) = \int \ud z \ud z'
    \delta(z - z') p(z) \sum_{l} \frac{2l+1}{4\pi} C_l^{zz}.
\end{equation}
